The impact of cosmic variance on simulating weak lensing surveys

### 2015-02-27 Writeup/reply.tex
do not repeat things you already said, just list anything not already mentioned

{\bf List of changes made}
\begin{enumerate}
\item Different linestyles are used in Figs.1-8 for the reader to be able to distinguish between the curves in black \& white, in response to referee's first comment.
\item A new paragraph has been added (in red color) towards the end of Sec. 4.2 in page 13, in response to the referee's second comment.
\item A new paragraph has been added (in red color) towards the end of page 12, in response to the referee's third comment. \\
\end{enumerate}

In addition to the above changes, we made a few minor modifications that are not in response to the referee's comments. \\

\begin{enumerate}\addtocounter{enumi}{3}
\item In Table 1, the overdense redshift bin 0.65-0.75 is now split into two bins, one from 0.65-0.7 and the other from 0.7-0.75. This is now in accordance
      with the other plots we show ( for example, Figs. 9-12)
\item We found a minor bug in the script that generated Fig.15 in the paper. We have fixed it.
\item We have thanked the referee in the `Acknowledgments' section for his/her useful comments.
\end{enumerate}

>>>>

In addition to the above changes, we found and fixed a minor bug in the script that generated
Fig.~15 in the paper.  The basic conclusions from that plot are, however, unchanged.
